Efficient Parallelization of $\ell_1$-Minimization for Face Recognition \thanks{Corresponding author: . This work was partially supported by ARO MURI W911NF-06-1-0076.}

### 2011-02-09 paper/main.tex
testing merge
revisions to lit review

@@

In a review paper by Allen Yang, they list 5 fast methods that solve $\ell_1$-minimization including gradient projection, homotopy, iterative shrinkage-thresholding, proximal gradient, and augmented lagrangian methods.  According to the review paper, they have determined that Homotopy and the Augmented Lagrangian Multiplier methods achieve the best recognition rates while maintaining a low computational cost.  A closer look at these two algorithms will show that

>>>>

\begin{figure}
\centering
\includegraphics[width=3.5in]{figures/runtime_graph.pdf}
\caption{GPU Alignment Stage Time vs. Size of Database}
\label{fig:alignment_runtime}
\end{figure}

@@

In a review paper by Allen Yang, they list 5 fast methods that solve $\ell_1$-minimization including gradient projection, homotopy, iterative shrinkage-thresholding, proximal gradient, and augmented lagrangian methods.  According to the review paper, they have determined that Homotopy and the Augmented Lagrangian Multiplier methods (ALM) achieve the best recognition rates while maintaining a low computational cost.  A closer look at these two algorithms will show that while the Homotopy method will produce the exact solution, the algorithm structure and functions do not lend themselves parallelization well.  On the other hand, the ALM algorithm computation mainly consists of matrix-vector operations, which lends itself to parallelization.
